### 2023-09-06 README.Rmd
release v1.0.5 (#506)

We welcome others helping us make this package as user-friendly and efficient as possible. Please review our [contributing](https://github.com/tidymodels/infer/blob/main/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/main/CONDUCT.md) guidelines. By participating in this project you agree to abide by its terms.

>>>>

We welcome others helping us make this package as user-friendly and efficient as possible. Please review our [contributing](https://github.com/tidymodels/infer/blob/main/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/main/.github/CODE_OF_CONDUCT.md) guidelines. By participating in this project you agree to abide by its terms.
